ACNP 2024 MS ANXIETY

### 2024-09-04 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_post_replication_prop_FINAL.Rmd
adding new figures

#save 
simple_demo_promis_diagnosis_df <- print(simple_demo_promis_diagnosis, as.data.frame = TRUE)
write.csv(simple_demo_all_groups_df, file = paste0(homedir, "/results/simple_demo_promis_diagnosis_df.csv"), row.names = TRUE)

@@

@@

##### BOX PLOT NO JITTER
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
  geom_boxplot(aes(fill = anxiety_severity), alpha = 0.3, outlier.size = 0) +  # Add boxplots with some transparency
#  geom_jitter(width = 0.2, size = 2, alpha = 0.8) +  # Add jittered points for individual observations
  scale_color_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
  scale_fill_viridis(discrete = TRUE, option = "D") +
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.x = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    panel.background = element_rect(colour = "white", fill = "white")
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")

###dot plot
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
  geom_point(position = position_jitter(width = 0.2, height = 0), size = 2, alpha = 0.8) +  # Individual data points with jitter
  stat_summary(fun = "mean", geom = "point", size = 4, shape = 21, fill = "black") +  # Mean points
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, color = "black") +  # Confidence intervals
  scale_color_viridis(discrete = TRUE, option = "D") +
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.x = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    panel.background = element_rect(colour = "white", fill = "white")
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")

>>>>

#save 
simple_demo_promis_diagnosis_df <- print(simple_demo_promis_diagnosis, as.data.frame = TRUE)
write.csv(simple_demo_promis_diagnosis_df, file = paste0(homedir, "/results/simple_demo_promis_diagnosis_df.csv"), row.names = TRUE)

@@

##### Box plot no jitter
```{r box_plot_no_jitter}

####
df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(anxiety_dose != -1) %>%
  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
  mutate(mean_UF_prop = mean_UF_prop*100)

# Define a custom palette
custom_colors <- c(

  #"MS+noA" = "#1F968B",
  #"MS+mildA" = "#39568C",
  #"MS+severeA" = "#482677" 
    #"MS+noA" = "#55C667",
  #"MS+mildA" = "#238A8D",
  #"MS+severeA" = "#404788" 
    #  "MS+noA" = "#404788",
#  "MS+mildA" = "#482677",
#  "MS+severeA" = "#440154" 
  #      "MS+noA" = "#1f968abf",
  #"MS+mildA" = "#33638d",
  #"MS+severeA" = "#482677" 
 #         "MS+noA" = "#29af7f",
#  "MS+mildA" = "#33638d",
#  "MS+severeA" = "#440154" 
            "MS+noA" = "#55c667",
  "MS+mildA" = "#2d708e",
  "MS+severeA" = "#440154" 
 # "MS+mildA" = viridis::viridis(3, option = "C")[2],  # Use green from 'D' for MS+noA
#  "MS+severeA" = viridis::viridis(3, option = "D")[1],  # Use a different color from 'D'
#  "MS+noA" = viridis::viridis(3, option = "D")[2]  # Use the last color from 'D'
)

##### BOX PLOT NO JITTER
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
  geom_boxplot(aes(fill = anxiety_severity), alpha = 0.65, outlier.size = 0) +  # Add boxplots with some transparency
    scale_color_manual(values = custom_colors) +  # Apply custom color scale
  scale_fill_manual(values = custom_colors) +  # Apply custom fill scale
#  geom_jitter(width = 0.2, size = 2, alpha = 0.8) +  # Add jittered points for individual observations
  #scale_color_viridis(discrete = TRUE, option = "C", direction = -1) +  # Use Viridis color scale
  #scale_fill_viridis(discrete = TRUE, option = "C", direction = -1) +
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.x = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    aspect.ratio = 7/6,
    panel.background = element_rect(colour = "white", fill = "white")
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")

@@

#save pdf
pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_box_plot_no_jitter.pdf"))
  prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
dev.off()

prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_horiz <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(y = anxiety_severity, x = mean_UF_prop, color = anxiety_severity)) +
  geom_boxplot(aes(fill = anxiety_severity), alpha = 0.65, outlier.size = 0) +  # Add boxplots with some transparency
#  geom_jitter(width = 0.2, size = 2, alpha = 0.8) +  # Add jittered points for individual observations
  scale_color_viridis(discrete = TRUE, option = "D", direction = -1) +  # Use Viridis color scale
  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1) +
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.x = element_text(size = 16, colour = "black"),
    axis.title.y = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    aspect.ratio = 5/6,
    panel.background = element_rect(colour = "white", fill = "white")
  ) + 
  labs(x = "Percent (%) of Uncinate Injured")
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_horiz

###### dot plot
```{r dot_plot_and_others}

df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(anxiety_dose != -1) %>%
  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
  mutate(mean_UF_prop = mean_UF_prop*100)

##plot
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
  geom_point(position = position_jitter(width = 0.2, height = 0), size = 2, alpha = 0.8) +  # Individual data points with jitter
  stat_summary(fun = "mean", geom = "point", size = 4, shape = 21, fill = "black") +  # Mean points
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, color = "black") +  # Confidence intervals
  scale_color_viridis(discrete = TRUE, option = "D") +
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.x = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    panel.background = element_rect(colour = "white", fill = "white")
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")
